---
title: 'Plotting for Manuscript: Seasonal Forecast Skill In Decision Variables'
author: "Ashish Kondal"
date: "04/09/2024"
output:
  pdf_document: default
  html_document: default
---


#-------------------------------------------------------------------------------
## 				SETUP - STARTING WITH FRESH ENVIRONMENT AND CONSOLE
#-------------------------------------------------------------------------------

```{r setup, include=FALSE}
knitr::opts_chunk$set(fig.width = 12, fig.height = 8, fig.path ='Figs/',echo = FALSE, warning = FALSE, message = FALSE)
cat("\014")     				# Clear console
rm(list = ls()) 				# Clearing the Environment and saved variable
```

## Installing Packages

#install.packages("dplyr")
#install.packages("data.table")
#install.packages("tidyverse")
#install.packages("pracma")
#install.packages("GGally")
#install.packages("reshape2")
#install.packages("Metrics")
#install.packages("ggpubr")
#install.packages("swfscMisc")
#install.packages("sf")



#-------------------------------------------------------------------------------
## 				LOADING PACKAGES
#-------------------------------------------------------------------------------
```{r Loading Packages, include = FALSE, echo = FALSE, warning=FALSE}
library(readr)		
library(knitr)
library(dplyr)
library(tidyverse)
library(ggplot2)
library(sf)
library(stringr)
```


#-------------------------------------------------------------------------------
## 				INPUT SETUP - DEFINE VARIABLES AND DIRECTORIES
#-------------------------------------------------------------------------------

```{r Input setup, echo=FALSE}
# Setting the working directory
wd <- setwd("YOUR INPUT PATH")

input_dir <- paste(wd,"/sample_data/", sep="")  			 # Setting input directory 
output_dir <- paste(wd,"/sample_data/output/", sep="") 		 # Setting output directory to store files and final images

if (!dir.exists(paste(output_dir, sep=""))){			# check if output directory already exists or not.
	dir.create(paste(output_dir, sep="")) }  			# Create output directory if not already exists

# Provide file path to the shapefiles
huc6_shapefile_address <- paste(wd,"/Shapefiles/PNW_Shapefile_USonly/pnw_shapefile_USonly.shp", sep="")		# PNW's shapefile at HUC06 Level
wa_shapefile_address <- paste(wd,"/Shapefiles/WA_Shapefile/WA_State_Boundary.shp", sep="")			# Shapefile of Washington state
or_shapefile_address <- paste(wd,"/Shapefiles/OR_Shapefile/Oregon.shp", sep="")					# Shapefile of Oregon state
id_shapefile_address <- paste(wd,"/Shapefiles/Idaho_shapefile/GU_StateOrTerritory.shp", sep="")			# Shapefile of Idaho state

# Reading shapefiles 
wa_shp = st_read(wa_shapefile_address)
or_shp = st_read(or_shapefile_address)
id_shp = st_read(id_shapefile_address)
huc6_shp = st_read(huc6_shapefile_address)
```


## 1. PNW's elevation dataset (Figure 1)
#-------------------------------------------------------------------------------
## 			EXTRACTING ELEVATION DATASET FOR US PORTION OF PNW (Figure 1)
#-------------------------------------------------------------------------------	
```{r Extracting Elevation Data }
# Reading elevation dataset 
elev_inputfilename <- paste(wd,"/sample_data/PNW_Elevation.txt",sep="") 						# path to elevation file	
elevation <- read_csv(file = elev_inputfilename,col_names = TRUE, show_col_types = FALSE)		# Reading elevation file

# Extracting elevation data for the US portion of the PNW region
HSS_inputfilename <- paste(input_dir, "GridWise_Tercile_HeidkeSkillScore_Fall_Fertilization_InitMonth_09_PNW_BothThreshold_NDJF.txt",sep="")  # Reading one of the skill metric files to get the spatial extent of PNW.	
HSS_data <- read_csv(file = HSS_inputfilename, col_names = TRUE, show_col_types = FALSE)						      # Reading above file
merged_data <- merge(HSS_data,elevation,by=c("Lat","Lon"))						# Merging elevation and skill metric data to remove all the grids that are not present in the skill metric file

# Saving the extracted elevation data in a text file for plotting in arcmap
elevation <- dplyr::select(merged_data,c("cell_id","Lat","Lon","Elevation"))					# select columns to save memory
elev_outputfilename <- paste(output_dir,"PNW_Elevation_inMeters_forUSportionOnly.txt",sep="") 			# Output elevation file name
write_csv(x = elevation, file = elev_outputfilename , append = FALSE, col_names = TRUE)			# Saving the elevation data for plotting later in arcmap.
rm(HSS_data,HSS_inputfilename,merged_data)
```
# Plot the elevation data (elev_outputfilename) in ArcMap

## 2. PNW's Cropland Grids (Figure 1)
#-------------------------------------------------------------------------------
## 		PNW's CROPLAND - IRRIGATED & NON-IRRIGATED GRIDS (Figure 1)
#-------------------------------------------------------------------------------	
```{r Cropland Grids}
# Reading the vegetation file
vegetation_file <- paste(wd,"/sample_data/PNW_crop_coverage_with_area_2024.txt",sep="")
vegetation <- read_csv(file=vegetation_file,col_names = TRUE, show_col_types = FALSE)

# Filter the irrigated and non-irrigated crop grids separately
veg_irrg <- filter(vegetation,(Crop_Code >= 100 & Crop_Code <10000))
veg_nonirrg <- filter(vegetation,(Crop_Code >= 10000))

# Saving the above data in separate text files - Plot in Arcmap 
veg_irrg_outputfilename <- paste(output_dir,"PNW_Irrigated_Croplands.txt",sep="")
veg_nonirrg_outputfilename <- paste(output_dir,"PNW_Non_Irrigated_Croplands.txt",sep="") 
write_csv(x = veg_irrg, file = veg_irrg_outputfilename, append = FALSE, col_names = TRUE)
write_csv(x = veg_nonirrg, file = veg_nonirrg_outputfilename, append = FALSE, col_names = TRUE)
```
# Plot the irrigated and non-irrigated croplands in ArcMap

#-------------------------------------------------------------------------------
## 	 Forecast Skill in Fall Fertilization Application Decision (Figure 3)
#-------------------------------------------------------------------------------	
```{r Plotting HSS of Fall Fertilizer Application for NDJF season on HUC 06 level, echo=FALSE, warning = FALSE}
# Removing previous runs data/variable
if (exists('dfdata') == TRUE){
			rm(dfdata)
}

# Running code for forecast initialized in November (11), October, September (9) and August (8)
for (init in c(11,10,9,8)){
  # Path to Heidke skill output file 
  HSS_inputfilename <- paste(input_dir, "HUC06_Tercile_HeidkeSkillScore_Fall_Fertilization_InitMonth_0",init,"_PNW_BothThreshold_NDJF.txt",sep="") 
	
  # Check if file exists in the input directory or not
  if (file.exists(HSS_inputfilename) == FALSE){
	  text0 <- paste("File Does not Exist !",HSS_inputfilename)
		print(text0)
	}else{
	  # Reading input file and removing NA's if any
		HSS_data <- read_csv(file = HSS_inputfilename,col_names = TRUE, show_col_types = FALSE)
		HSS_data <- na.omit(HSS_data)
		
		# Converting Initialization Month into Lead-Month 
		lookt <- c(0,0,0,0,0,-5,-4,-3,-2,-1,0,0)  # Look out table
    init1 =  lookt[init]                      # Based on the look out table, initialization month is converted into lead month.
    HSS_data['Init'] <- factor(init1)					
    
    # Creating new variable to append HSS data for all initialization together
		if (exists('dfdata') != TRUE){            # if 'dfdata' doesn't exist, create this variable and save the HSS file's data in it.
			dfdata <- HSS_data
			rm(HSS_data)
		}else{                                    # if 'dfdata' already exist, append the HSS file's data from other intializations to it.
			dfdata <- rbind(dfdata,HSS_data)        # This is the reason, we ensured that 'dfdata' shouldn't exists (if exists for any reason, remove it) at the beginning of this code chunk.
			rm(HSS_data)
		}
    
	}  
}   

dfdata$Init <- factor(dfdata$Init, levels = c(0,-1,-2,-3))            # Factoring the lead months and ordering them for plotting purposes

# Select desired columns for the data and rename it for the plotting purposes
dfdata <- dplyr::select(dfdata,c("Init","HUC06_Name","Below 33rd Percentile","Above 67th Percentile"))
colnames(dfdata) <- c("Init","Name","Forecast of Cold Winters","Forecast of Warm Winters")

# Format the data in long format for easy plotting using "facet_grid"
dfdata_short <- dfdata %>% pivot_longer(!c("Name","Init"),names_to="Group",values_to ="Value")

# Merging the above data with HUC06  shapefile by "Name". This is done to geospatially connect the "dfdata_short" with "huc6_shp"
data_merged <- merge(huc6_shp,dfdata_short,by='Name')

# Final Plot
ggfilename <- paste(output_dir,"HUC06_SpatialMaps_HSS_ENSMEAN_Fall_Fertilization_PNW_NDJF.jpeg",sep = "")  # output figure's name
plot1 <- ggplot() + geom_sf(data = data_merged, aes(fill = Value)) +
                  scale_fill_gradientn(colours=c("orangered4","brown4","chocolate","yellow","white","green","darkgreen","darkblue","darkviolet"),
                            n.breaks=10,limits = c(-100,100), name='Heidke Skill Score') +
      						facet_grid(Group ~ Init,switch="y",labeller=label_wrap_gen(11))+ scale_x_continuous(breaks = seq(-125, -109, by = 3))+
                  scale_y_continuous(breaks = seq(40, 54, by = 2),position='left')+
      		  	    geom_sf(data = huc6_shp, mapping = aes(fill = OBJECTID), color = alpha("black",0.5),size = 0.5, fill = NA) +
      				   	ylab("Seasons") + theme_bw() + 
                  theme(strip.placement = 'outside',panel.spacing.x = unit(0.2,"cm"), axis.text=element_text(size=11,face="bold"),
                        axis.text.x=element_text(angle=90,size=11,face="bold"),axis.title.x = element_blank(), axis.title.y =element_blank(),
                        panel.grid.major = element_blank(),panel.grid.minor = element_blank(), legend.title = element_text(angle =0,size=11,face='bold'),
                        legend.text = element_text(size=13),legend.position="bottom",legend.title.align = 0.5,
                        strip.text = element_text(size=13,face="bold"))+
                  guides(reverse = TRUE,fill =guide_colourbar(barwidth =35, barheight =1,title.position = "bottom"))+
        jpeg(filename=ggfilename, bg="white", width=7000, height=3500, pointsize=15, res=600, quality=100)

plot(plot1)
dev.off()
rm(dfdata,data_merged)

```

#-------------------------------------------------------------------------------
## 	BAR PLOT - HSS FALL FERTILIZATION  (Figure 4)
#-------------------------------------------------------------------------------	

```{r HSS Vegetation}
# Reading vegetation file
vegetation_file <- paste(input_dir,"PNW_crop_coverage_with_area_2024.txt",sep="")
vegetation <- read_csv(file=vegetation_file,col_names = TRUE, show_col_types = FALSE,
                       col_select = c("Cell_id","Crop_Code","Crop_Frac","Grid_area_km2","Crop_area_km2"))
colnames(vegetation) <- c("cell_id","Crop_Code","Crop_Frac","Grid_area_km2","Crop_area_km2")

# Extract irrigated and non-irrigated cropland separately
veg_irrg <- filter(vegetation,(Crop_Code >= 100 & Crop_Code <10000))
veg_nonirrg <- filter(vegetation,(Crop_Code >= 10000))


# Removing previous runs data/variable
if (exists('dfdata_bin') == TRUE){
			rm(dfdata_bin)
}

# Running code for forecast initialized in November (11), October (10), September (9) and August (8)
for (init in c(11,10,9,8)){
  # Path to Heidke skill output file which will be used as input for this code chunk 
  HSS_inputfilename <- paste(input_dir, "GridWise_Tercile_HeidkeSkillScore_Fall_Fertilization_InitMonth_0",init,"_PNW_BothThreshold_NDJF.txt",sep="")		
  
  # Check if file exists in the input directory or not
  if (file.exists(HSS_inputfilename) == FALSE){
    text0 <- paste("File Does not Exist !",HSS_inputfilename)
  	print(text0)
  }else{
    # Reading input file and removing NA's if any
    HSS_data0 <- read_csv(file = HSS_inputfilename, col_names = TRUE, show_col_types = FALSE)						
    colnames(HSS_data0) <- c("Lat","Lon","Below_33rd_Percentile","Between","Above_67th_Percentile")
		HSS_data0 <- na.omit(HSS_data0)
		
		# Merge Elevation data to attach "cell_id" to HSS data based on "Lat" and "Lon"
		HSS_data1 <- merge(HSS_data0,elevation,by=c("Lat","Lon"))			 
		
		#STEP1: Extract Only Irrigated Grid Cells 
		HSS_data2 <- merge(HSS_data1,veg_irrg,by="cell_id",all.x=TRUE)
    HSS_data2 <- na.omit(HSS_data2)	
		HSS_data2['Category'] <- as.factor("Irrigated")   # Make a new column named "Category" and fill it up with management type i.e. "Irrigated"
		
		#STEP2: Generate weighted mean HSS (multiply irrigated crop_area of individual grids to HSS and then divide it with total area of irrigated grids)
		HSS_data2['B33'] <- HSS_data2$Below_33rd_Percentile * HSS_data2$Crop_area_km2     # For Below 33rd percentile category
		HSS_data2['A67'] <- HSS_data2$Above_67th_Percentile * HSS_data2$Crop_area_km2     # For Above 67th percentile category
		HSS_data3 <- HSS_data2 %>% group_by(Category) %>% 
		  summarize("Forecast of Cold Winters" = sum(B33)/sum(Crop_area_km2),"Forecast of Warm Winters" = sum(A67)/sum(Crop_area_km2))
		
		
		## Repeat above steps (STEP1 & STEP2) for non-irrigated cropgrids 
		
		# Extract Only Non-Irrigated Grid Cells 
		HSS_data4 <- merge(HSS_data1,veg_nonirrg,by="cell_id",all.x=TRUE)
    HSS_data4 <- na.omit(HSS_data4)	
		HSS_data4['Category'] <- as.factor("Non Irrigated") 	# Make a column named "Category"  --> as.factor(Non-Irrigated)
		
	  #Generate weighted mean HSS (multiply non-irrigated crop_area of individual grids to HSS and then divide it with total area of Non-irrigated grids)
		HSS_data4['B33'] <- HSS_data4$Below_33rd_Percentile * HSS_data4$Crop_area_km2
		HSS_data4['A67'] <- HSS_data4$Above_67th_Percentile * HSS_data4$Crop_area_km2
		HSS_data5 <- HSS_data4 %>% group_by(Category) %>%
		  summarize("Forecast of Cold Winters" = sum(B33)/sum(Crop_area_km2),  "Forecast of Warm Winters" = sum(A67)/sum(Crop_area_km2))
		
		# Join above data frames (Irrigated and Non-irrigated) row-wise i.e. use "rbind"
	  bin_data <- rbind(HSS_data3,HSS_data5)
  	rm(HSS_data2,HSS_data4,HSS_data3,HSS_data5)
  	
	  # Make Column Named "Init" to save Lead month --> converted from initialization month
		lookt <- c(0,0,0,0,0,-5,-4,-3,-2,-1,0,0)    # Look out table
    init1 =  lookt[init]                        # Based on the look out table, initialization month is converted into lead month.
    bin_data['Init'] <- factor(init1)		
  	
    # Creating new variable to append HSS data for all initialization together
    if (exists('dfdata_bin') != TRUE){            # if 'dfdata_bin' doesn't exist, create this variable and save the above data in it.
  	  dfdata_bin <- bin_data
  		rm(bin_data)
  	}else{                                        # if 'dfdata_bin' already exist, append the data from other intializations to it.
  		dfdata_bin <- rbind(dfdata_bin,bin_data)    # This is the reason, we ensured that 'dfdata_bin' shouldn't exists (if exists for any reason, remove it) at the beginning of this code chunk.
  		rm(bin_data)
  	}
  }
}  

# Removing any NA's 
dfdata_bin <- na.omit(dfdata_bin)

dfdata_bin$Init <- factor(dfdata_bin$Init, levels = c(0,-1,-2,-3))                       # Factoring the lead months and ordering them for plotting purposes
dfdata_bin$Category <- factor(dfdata_bin$Category,levels=c("Irrigated","Non Irrigated")) # Factoring the "category" column and ordering it for plotting purposes

# Format the data in long format for easy plotting using "facet_grid"
dfdata_short <- dfdata_bin %>% pivot_longer(!c("Category","Init"),names_to="Threshold",values_to ="HSS")

# Final Plot
ggfilename <- paste(output_dir,"Fall_Fertilization_HSS_VEGETATION_Correlation_BINNED_Bargraph_NDJF.jpeg",sep = "")  # output figure's name
plot1 <- ggplot(data = dfdata_short, aes(x= str_wrap(Category,width=9), y= HSS,fill = Category))+
              geom_bar(stat="identity",width=0.5,color=c("darkblue"))+scale_fill_manual(values=c("blue","darkgreen"))+
              facet_grid(Threshold ~ Init,switch="y",labeller=label_wrap_gen(11))+
  		      	xlab("Category") +	ylab("Initializaiton") + theme_bw() + 
              theme(strip.placement = 'outside',panel.spacing.x = unit(0.2,"cm"), axis.text=element_text(size=11,face="bold"),
                    axis.text.x=element_text(angle=0,size=8,face="bold"), axis.title.x = element_blank(), axis.title.y =element_blank(),
                    panel.grid.major = element_blank(),panel.grid.minor = element_blank(),
                    legend.title = element_text(angle =270,size=18,face='bold'),
                    legend.text = element_text(size=18),legend.title.align = 0.5,strip.text = element_text(size=18,face="bold"))+
              guides(reverse = TRUE,fill =guide_colourbar(barwidth = 1, barheight = 20,title.position = "right"))+
  		        jpeg(filename=ggfilename, bg="white", width=2500, height=1500, pointsize=13, res=300, quality=100)
  		
plot(plot1)
dev.off()
rm(plot1, dfdata_bin,dfdat_short)
```

#-------------------------------------------------------------------------------
## 	Forecast Skill in Predicting Drought Based on the Regional Water Supply  (Figure 5)
#-------------------------------------------------------------------------------	
```{r Drought Response, echo=FALSE, warning = FALSE}
# Removing previous runs data/variable
if (exists('dfdata') == TRUE){
			rm(dfdata)
}

# Running code for forecast initialized in April, March, February and January
for (init in c(4,3,2,1)){
 
  # Path to Heidke skill output file 
  HSS_inputfilename <- paste(input_dir,"HUC06_HeidkeSkillScore_Accumulated_Baseflow_Runoff_InitMonth_0",
                               init,"_PNW_AMJJAS_75percentMedian_BothThreshold.txt",sep="")
	
  # Check if file exists in the input directory or not
  if (file.exists(HSS_inputfilename) == FALSE){
	  text0 <- paste("File Does not Exist !",HSS_inputfilename)
		print(text0)
	}else{
    # Reading input file and removing NA's if any
	  HSS_data <- read_csv(file = HSS_inputfilename,col_names = TRUE, show_col_types = FALSE,col_select = c("Name","BinaryForecast_75percentMedian"))
  	HSS_data <- na.omit(HSS_data)
  	
		# Converting Initialization Month into Lead-Month   	
  	lookt <- c(-3,-2,-1,0,0,0,0,0,0,-6,-5,-4)  # Look out table
  	init1 =  lookt[init]                      # Based on the look out table, initialization month is converted into lead month.
    HSS_data['Init'] <- factor(init1)						
  	
    # Creating new variable to append HSS data for all initialization together
    if (exists('dfdata') != TRUE){            # if 'dfdata' doesn't exist, create this variable and save the HSS file's data in it.
  	  dfdata <- HSS_data
  		rm(HSS_data)
  	}else{                                    # if 'dfdata' already exist, append the HSS file's data from other intializations to it.
  	  dfdata <- rbind(dfdata,HSS_data)        # This is the reason, we ensured that 'dfdata' shouldn't exists (if exists for any reason, remove it) at the beginning of this code chunk.
  		rm(HSS_data)
  	}
	}
}  

dfdata$Init <- factor(dfdata$Init, levels = c(0,-1,-2,-3))            # Factoring the lead months and ordering them for plotting purposes

# Merging the above data with HUC06  shapefile by "Name". This is done to geospatially connect the "dfdata_short" with "huc6_shp"
data_merged <- merge(huc6_shp,dfdata,by='Name')

# Final Plot
ggfilename <- paste(output_dir,"HUC06_SpatialMaps_HSS_DroughtResponse_AMJJAS.jpeg",sep = "")  # output figure's name
plot1 <- ggplot() + geom_sf(data = data_merged, aes(fill = BinaryForecast_75percentMedian)) +
                  scale_fill_gradientn(colours=c("orangered4","brown4","chocolate","yellow","white","green","darkgreen","darkblue","darkviolet"),
                            n.breaks=10,limits = c(-100,100), name='Heidke Skill Score') +
      						facet_grid(~ Init,switch="y",labeller=label_wrap_gen(11))+ scale_x_continuous(breaks = seq(-125, -109, by = 3))+
                  scale_y_continuous(breaks = seq(40, 54, by = 2),position='left')+
      		  	    geom_sf(data = huc6_shp, mapping = aes(fill = OBJECTID), color = alpha("black",0.5),size = 0.5, fill = NA) +
      				   	ylab("Seasons") + theme_bw() + 
                  theme(strip.placement = 'outside',panel.spacing.x = unit(0.2,"cm"), axis.text=element_text(size=11,face="bold"),
                        axis.text.x=element_text(angle=90,size=11,face="bold"),axis.title.x = element_blank(), axis.title.y =element_blank(),
                        panel.grid.major = element_blank(),panel.grid.minor = element_blank(), legend.title = element_text(angle =0,size=11,face='bold'),
                        legend.text = element_text(size=13),legend.position="bottom",legend.title.align = 0.5,
                        strip.text = element_text(size=13,face="bold"))+
                  guides(reverse = TRUE,fill =guide_colourbar(barwidth =35, barheight =1,title.position = "bottom"))+
        jpeg(filename=ggfilename, bg="white", width=7000, height=3500, pointsize=15, res=600, quality=100)
plot(plot1)
dev.off()
rm(dfdata,data_merged,plot1)
``` 

#-------------------------------------------------------------------------------
## 	Forecast Skill in Drought Response - Yakima Basin  (Figure 6)
#-------------------------------------------------------------------------------

## Spatial Maps of Drought Response of Others Basins - Lead 0 - HSS, Elevation, Actual runoff+baseflow
```{r Gridwise Binary Drought Response Spatial Maps - Others, echo=FALSE, warning = FALSE}

#-------------------------------------------------------------------------------
## 			FUNCTION FOR SPATIAL OPERATIONS
#-------------------------------------------------------------------------------

perform_spatial_operations <- function(current_huc_name, full_huc_shapefile, data_transformed_as_sf) {
	nam1 <- subset(full_huc_shapefile, Name == current_huc_name)															# Subset the HUC06 file to extract current sub-basin's shapefile.
	shp1 = st_transform(structure(nam1, proj4string = "+init=epsg:3857"), "+init=epsg:4326")	# Transform the projection of subsetted sub-basin's shapefile
	intersect_ind =st_intersects(data_transformed_as_sf, shp1, sparse=FALSE)									# Finding row index of coordinates in sf_data (i.e. merged_data) which falls within sub-basin. 
	data_hucc = data_transformed_as_sf[intersect_ind,]																				# Extracting data from sf_data based on "intersect_ind".
	df_data_huc <- st_drop_geometry(data_hucc)
  df_data_huc <- na.omit(df_data_huc)															            							# Removing NA's in the data
	return(df_data_huc)
}


ggfilename <- paste(output_dir,"YK_SpatialMaps_DroughtResponse_GridWiseHSS_Elevation_ActualRunoffBaseflow_AMJJAS.jpeg",sep = "")  # output figure's name

# Reading Input file of Grid level HSS --> Binary forecast of Drought or non-drought 
HSS_inputfilename <- paste(input_dir, "GridWise_BinaryThreshold_HeidkeSkillScore_Drought_Response_InitMonth_04_PNW_75percentMedian_BothThreshold.txt",sep="")
HSS_data <- read_csv(file = HSS_inputfilename,col_names = TRUE, show_col_types = FALSE)
HSS_data <- na.omit(HSS_data) # Removing NA's if any

# Merge Elevation data to HSS data based on "Lat" and "Lon"
elevation1 <- merge(HSS_data,elevation, by=c("Lat","Lon"))
elevation1$Lat1 <- elevation1$Lat     # Duplicating Latitudes in a new variable "Lat1". This is done to ensure Latitude information in a later steps.
elevation1$Lon1 <- elevation1$Lon     # Duplicating Longitudes in a new variable "Lon1". This is done to ensure Longitude information in a later steps.

# Transforming merged data into a shapefile for subsequent processing. 
sf_data = st_as_sf(elevation1, coords = c("Lon", "Lat"),crs=4326)		# During this step, "Lat" and "Lon" becomes inaccessible. This is why we have duplicated them in earlier steps. 

# Extracting data for Yakima Basin only
name_huc <- huc6_shp$Name	              # Name of all the basins at HUC06 levels
current_huc <- name_huc[11]							# Current Sub-basin i.e.Yakima. This is hardcoded for Yakima.
df_data_huc <- perform_spatial_operations(current_huc, huc6_shp, sf_data)		# Perform spatial operation on current sub-basin and extracting data for Yakima.

# Extracting the geographical extent of Yakima
Lat_min <- round(min(df_data_huc$Lat1))
Lat_max <- round(max(df_data_huc$Lat1))
Lon_min <- round(min(df_data_huc$Lon1))
Lon_max <- round(max(df_data_huc$Lon1))
# Extracting Yakima's shapefile from the PNW's HUC06 shapefile
polygon_to_plot <- huc6_shp[huc6_shp$Name == current_huc, ]
polygon_to_plot <- st_transform(polygon_to_plot,crs=4326)
mapRange1 <- st_bbox(polygon_to_plot)

# Plotting HSS for Yakima River Basin at Lead 0 i.e. HSS for April intialized forecast
plot1 <- ggplot()+ geom_tile(data = df_data_huc, aes(x = Lon1, y = Lat1, fill = HeidkeSkillScore_DroughtVsNonDrought)) +
               scale_fill_gradientn(colours=c("orangered4","brown4","chocolate","darkorange","grey50","darkgreen","cyan","darkblue","darkviolet"),
                                              n.breaks=10,limits = c(-100,100), name='Heidke Skill Score')+
					    scale_x_continuous(breaks = seq(Lon_min,Lon_max, by = 1))+ scale_y_continuous(breaks = seq(Lat_min,Lat_max, by = 0.5),position='left')+
              geom_sf(data = polygon_to_plot, mapping = aes(fill = OBJECTID), color = alpha("black",0.5),size = 0.5, fill = NA) +
              coord_sf(xlim = mapRange1[c(1,3)], ylim = mapRange1[c(2,4)])+ 
              theme_bw() + theme(strip.placement = 'outside',panel.spacing.x = unit(0.2,"cm"), axis.text=element_text(size=13,face="bold"),
					                       axis.text.x=element_text(angle=0,size=13,face="bold"),axis.title.x = element_blank(), axis.title.y =element_blank(),
					                       panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="bottom",
					                       legend.title = element_text(angle =0,size=13,face='bold'), legend.text = element_text(size=13),
					                       legend.title.align = 0.5,strip.text = element_text(size=13,face="bold"))+
              guides(reverse = TRUE,fill =guide_colourbar(barwidth = 18, barheight = 1,title.position = "bottom")) 
# Plotting Elevation map of Yakima
plot2 <- ggplot()+geom_tile(data = df_data_huc, aes(x = Lon1, y = Lat1, fill = Elevation)) +
               scale_fill_gradientn(colours=c("lightskyblue","slategray3","lemonchiffon","salmon1","tomato1","tomato4"),
                                              n.breaks=6,breaks = c(1,500,1000,1500,2000,2500,3300),name='Elevation')+ 
              scale_x_continuous(breaks = seq(Lon_min,Lon_max, by = 1))+ scale_y_continuous(breaks = seq(Lat_min,Lat_max, by = 0.5),position='left')+
              geom_sf(data = polygon_to_plot, mapping = aes(fill = OBJECTID), color = alpha("black",0.5),size = 0.5, fill = NA) +
              coord_sf(xlim = mapRange1[c(1,3)], ylim = mapRange1[c(2,4)])+ 
					    theme_bw() + theme(strip.placement = 'outside',panel.spacing.x = unit(0.2,"cm"), axis.text=element_text(size=13,face="bold"),
					                       axis.text.x=element_text(angle=0,size=13,face="bold"),axis.title.x = element_blank(), axis.title.y =element_blank(),
					                       panel.grid.major = element_blank(), panel.grid.minor = element_blank(), legend.position="bottom",
					                       legend.title = element_text(angle =0,size=13,face='bold'), legend.text = element_text(size=13),
					                       legend.title.align = 0.5,strip.text = element_text(size=13,face="bold"))+
              guides(reverse = TRUE,fill =guide_colourbar(barwidth = 18, barheight = 1,title.position = "bottom")) 
# Arrange the HSS and Elevation map row-wise and saving it
plot4 <- egg::ggarrange(plot1,plot2, nrow=1)
ggsave(filename = ggfilename,plot=plot4,height=5,width=12,units="in",dpi=1200)
rm(plot4,plot1,plot2,df_data_huc)
``` 
